A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-24 text/introduction.tex
Fix order.

Multi-stage programming makes it easier for programmers to implement
generation and execution of code at run time by providing language
constructs for composing and running pieces of code as first-class
values.  A promising application of multi-stage programming is
(run-time) code specialization, which is to generate program code
specialized to partial inputs to the program and such applications are
studied in the literature~\cite{8384206,taha2007gentle}  
% \AI{We should list applications of multi-stage programming, not necessarily of MetaOCaml.}

>>>>

Multi-stage programming makes it easier for programmers to implement
generation and execution of code at run time by providing language
constructs for composing and running pieces of code as first-class
values.  A promising application of multi-stage programming is
(run-time) code specialization, which is to generate program code
specialized to partial inputs to the program and such applications are
studied in the literature~\cite{8384206,mainland2012metahaskell,taha2007gentle}.
% \AI{We should list applications of multi-stage programming, not necessarily of MetaOCaml.}
